Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2013-02-01 doc/asplos13/paper.tex
initial methodology section
Added initial implementation discussion
add evaluation section, start to UTS subsection/plot
pass on abs,intro
add acknowledgements
paper checklist from asplos13 cfp
more checklist
formatting job
Super redux
removing TODOs
merge conflicts
minor stuff
Remove redundant 'references' section (Preston)

\input{header}

\begin{document}

\title{All Your Graphs Belong to Us}
\author{TBD}

@@

\input{whynot}

\input{grappa}

\subsection{References}
\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\input{header}
\usepackage{microtype}
\begin{document}

\title{Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications}
%\title{All Your Graphs Belong to Us}
%\authorinfo{\vspace{-2ex}Anonymous for review\vspace{-6ex}}{}{}
\authorinfo{Jacob Nelson$^{\dagger}$,
  Brandon Holt$^{\dagger}$,
  Brandon Myers$^{\dagger}$,
  Preston Briggs$^{\dagger}$,
  Luis Ceze$^{\dagger}$,
  Simon Kahan$^{{\dagger \ddagger}}$,
  Mark Oskin$^{\dagger}$
}{\textdagger University of Washington, \textdaggerdbl Pacific Northwest National Laboratory}{
  \{nelson, bholt, bdmyers, preston, luisceze, skahan, oskin\}@cs.washington.edu}

@@

\input{relatedwork}

\input{overview}

\input{tasks}

\input{memory}

\input{communication}

\input{method}

\input{evaluation}

\input{conclude}

%\input{acknowledgements}

%\subsection{References}
\bibliographystyle{abbrv}
\bibliography{paper}
